{\fontfamily{ptm}\selectfont The Proximal Point interpretation of Nesterov accelerated proximal gradient}

### 2024-08-15 Notebook LaTEX/Momentum Accelerations/paper.tex
/w\, work home sync
=w=, a lot of changes

\section{Introduction}
    Recent works from Ahn and Sra \cite{ahn_understanding_2022} and Nesterov \cite{nesterov_lectures_2018} inspired content in this section.
    They explored the interpretation of Nesterov acceleration as a proximal of an upper surrogate function, and then a lower surrogate function. 
    Inspired by such an interpretation, we generalize the framework to the case of $h = f + g$ with $f$ Lipschitz smooth and $g$ convex and friendly to a proximal operator. 
    \par
    Classical analysis and extension of Nesterov accelerated gradient existed. 
    See \cite*{guler_new_1992} for an extension of the Nesterov accelerated gradient method to the proximal point method for convex programming. 
    However the classical analysis found in \cite*[chapter 2]{nesterov_lectures_2018} involves the assumption of a specific kind of Lypunov function and cherry picked Nesterov's estimating sequence to assist the proof for the parameters in the algorithm. 
    In Ahn's work however, the complexities are packaged into the PPM interpretation of accelerated gradient. 
    It uses a lemma from Moreau envelope to derive the Lypunov analysis, the sizes, and parameters for several variants of the algorithm. 
    \par
    Numerous notable variations of Nesterov accelerated gradient exists. \cite*[(6.1.19)]{nesterov_lectures_2018} described a variant of accelerated gradient restricted to a convex domain $Q$. 
    Beck and Toubolle \cite{beck_fast_2009} introduced a variant the problem type of smooth plus non-smooth, known as FISTA. 
    For a variant of accelerated gradient where the iterates converge, see \cite{chambolle_convergence_2015}. 
    Extension such as the Harpen acceleration for the resolvent operator in general is outside of the scope since doesn't have a Moreau envelope. 
    \par
    A wide varieties of interpretation for the Nesterov accelerated gradient exist in the literatures. 
    Consult \cite{su_differential_2015} for a dynamical system interpretation of Nesterov acceleration. 
    The dynamical system interpretation of the algorithm however, lead to the valuable insights that restarting the accerlated gradient algorithm would lead to faster convergence rate for the class of strongly convex function. 
    \par
    % The paper is organized as follow: 
    % \begin{enumerate}
    %     \item Section 
    % \end{enumerate}

\section{Preliminaries}\label{sec:preliminaries}
    Fristly, recall the theorem: 
    \begin{theorem}[Proximal Descent Inequality]\label{thm:ppm_descent_ineq}
        With $f: \RR^n \mapsto \overline \RR^n$ $\beta$ stronly convex where $\beta \ge 0$, fix any $x \in \RR^n$, let $p = \hprox_f(x)$, then for all $y$ we have inequality 
        $$
            \left(f(p) + \frac{1}{2}\Vert x - p\Vert^2\right)
            - 
            \left(
                f(y) + \frac{1}{2}\Vert x - y\Vert^2 
            \right)
            \le 
            - \frac{(1 + \beta)}{2}\Vert y - p\Vert^2. 
        $$
        Recall: $\hprox_f(x) = \argmin_{u}\left\lbrace f(u) + \frac{1}{2}\Vert u - x\Vert^2 \right\rbrace$. 
    \end{theorem}
    \begin{remark}
        We use this theorem to prove the convergence of the proximal point method. 
        See the proof (\cite{bauschke_convex_2017}, theorem 12.26). 
    \end{remark}
    We introduce some additional lemma that are crucial to the derivations of non-smooth accelerated gradient method. 
    \begin{definition}[The Gradient Mapping]
        \label{def:gradient_mapping}
        Let $g = f + g$ where $f$ is $L$-Lipschitz smooth and convex, $g$ is convex. 
        Define the proximal gradient operator
        $$
            \mathcal T_L(x) := \hprox_{L^{-1}g}(x - L^{-1}\nabla f(x)),
        $$
        then the gradient mapping is defined as
        $$
            \mathcal G_L(x) = L(x - \mathcal T_L(x)). 
        $$
    \end{definition}
    \begin{remark}
        The name ``gradient mapping" comes from \cite[(2.2.54)]{nesterov_lectures_2018}, however, Nesterov was referring to only the case when $g$ is an indicator function of a convex set in his writing. 
        Of course, in Amir Beck \cite[10.3.2]{beck_first-order_nodate}, it has the exact same definition for gradient mapping as the above. 
    \end{remark}

    \begin{lemma}[Gradient Mapping Approximates Subgradient]
        \label{lemma:grad_map_lemma_first}
        Continue from 
        \hyperref[def:gradient_mapping]{definition \ref*{def:gradient_mapping}}, 
        the gradient mapping satisfies
        \begin{align*}
            x^+ &= \mathcal T_L(x), 
            \\
            L(x - x^+) &\in  \nabla f(x) + \partial g(x^+) \ni \mathcal G_L(x). 
        \end{align*}
    \end{lemma}
    \begin{proof}
        \begin{align*}
            x^+ &= [I + L^{-1}\partial g]^{-1}\circ [I - L^{-1}\nabla f](x)
            \\
            [I + L^{-1}\partial g](x^+) &\ni [I - L^{-1}\nabla f](x)
            \\
            x^+ + L^{-1}\partial g(x^+) &\ni x - L^{-1}\nabla f(x)
            \\
            x^+ - x + L^{-1}\partial g(x^+) &\ni L^{-1}\nabla f(x)
            \\
            L(x^+ - x) + \partial g(x^+) &\ni - \nabla f(x)
            \\
            L(x - x^+) &\in \nabla f(x) + \partial g(x^+)
            \\
            \mathcal G_L(x) &\in \nabla f(x) + \partial g(x^+). 
        \end{align*}
    \end{proof}

@@

        Continue from 
        \hyperref[lemma:grad_map_lemma_first]{definition \ref*{lemma:grad_map_lemma_first}}, 
        further assume that $f$ is strongly convex with index $\mu \ge 0$,
        with $x^+ = \mathcal T_L(x)$, the gradient mapping satisfies the inequality for all $z$: 

@@

        Directly from the $L$-smoothness of $f$, convexity of $g, f$, we have the list of inequalities: 

@@

        Then we have the following sequence of relations 

@@

@@

\section{The PPM interpreation of accelerated gradient}\label{sec:ppm_interp_of_ag}
    In this section, we state the PPM formulation of the accelerated proximal gradient method. 
    The formulation is abstract because the parameters are not yet determined. 
    \begin{definition}[AG Proximal Gradient PPM Generic Form]
    \label{def:ag_prox_grad_ppm}
        Let $h=f + g$ be the sum of convex function $g$ and convex differentiable $f$ with $L$-Lipschitz gradient. 
        With $\mathcal T_L, \mathcal G_L$ being the proximal gradient, and the gradient mapping operator. 
        Define the linear lower bounding function for $h$ at $y$, for all $x$: 
        $$
        \begin{aligned}
            l_h(x; y) &= h(\mathcal T_L y) + \langle \mathcal G_L(y), x - y \rangle 
                + \frac{L}{2}\Vert y - \mathcal T_L y\Vert^2
            \le h(x), 
        \end{aligned}
        $$
        with that we define the algorithm:
        $$
        \begin{aligned}
            x_{t + 1} &= \argmin_{x} \left\lbrace
                l_h(x; y_t) + \frac{1}{2\tilde \eta_{t + 1}} 
                \Vert x - x_t\Vert^2
            \right\rbrace,
            \\
            y_{t + 1}&= 
            \argmin_{x}
            \left\lbrace
                l_h(x; y_t) + \frac{L}{2}\Vert x - y_t\Vert^2 + 
                \frac{1}{2\eta_{t + 1}} \Vert x - x_{t + 1}\Vert^2
            \right\rbrace.
        \end{aligned}
        $$
    \end{definition}

    \begin{definition}[AG Proximal Gradient Generic Form]
    \label{def:ag_prox_grad_generic}
        With $h = f + g$, where $g$ is convex, $f$ is convex and $L$-Lipschitz smooth. 
        Define $x^+ = \mathcal T_L(x)$, so that $\mathcal G_L(x) = L(x -  x^+)$, we define the algorithm updates $(y_t, x_{t + 1}, z_{t + 1})$ with expression: 
        $$
        \begin{aligned}
            y_t^+ &= \mathcal T_L(y_t)
            \\
            y_t &= (1 + L\eta_t)^{-1}(x_t + L\eta_t z_t)
            \\
            x_{t + 1} &= x_t - \tilde \eta \mathcal G_L(y_t)
            \\
            z_{t + 1} &= y_t - L^{-1}\mathcal G_L(y_t)
        \end{aligned}
        $$
        for all $t\in \mathbb N$ where the base case has $y_0 = x_0$. 
    \end{definition}
    \begin{remark}
        Observe that $z_{t + 1} = y_t^+$. 
    \end{remark}

    \begin{proposition}[Deriving Proximal Gradient Generic Form]
        \label{prop:derive_ag_prox_grad_tript}
        \quad \\
        Continue from the proximal point interpretation of the proximal gradient 
        (\hyperref[def:ag_prox_grad_ppm]{definition \ref*{def:ag_prox_grad_ppm}})
        we have the equalities 
        \begin{align*}
            x_{t + 1} &= \argmin_{x}
            \left\lbrace
                l_h(x, y_t) + \frac{1}{2\tilde \eta_{t + 1}} \Vert x - x_t\Vert^2
            \right\rbrace
            \\
            &= x_t - \tilde\eta_{t + 1} \mathcal G_L(y_t), 
            \\
            y_{t + 1} &= \argmin_{x}
            \left\lbrace
                    h(y_t^+) + \langle \mathcal G_L(y_t), x - y_t\rangle + \frac{L}{2}\Vert x -y_t\Vert^2 + \frac{1}{2\eta_{t + 1}}\Vert x - x_{t + 1}\Vert^2
            \right\rbrace
            \\
            &= (1 + L\eta_{t + 1})^{-1}
            (x_{t + 1} + L\eta_{t + 1}(y_t - L^{-1}\mathcal  G_L(y_t))). 
        \end{align*}
        Therefore, the algorithm in
        \hyperref[def:ag_prox_grad_ppm]{definition \ref*{def:ag_prox_grad_ppm}}
        is equivalent to algorithm in
        \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}}
    \end{proposition}
    \begin{proof}
        Let $y_t^+ = \mathcal T_L(y_t)$, recall that $l_h(x; y_t) = h(y_t^+) + \langle \mathcal G_L(y_t), x -y_t\rangle \le f(x)$ by the definition of algorithm. 
        Since $l_h(x; y_t)$ is a simple linear function wrt $x$, minimizing the quandratic where to get $x_{t + 1} = x_t - \tilde\eta_{t + 1} \mathcal G_L(y_t)$; for $y_{t + 1}$, complete the square on the second and the third terms: 
        \begin{align*}
            & \frac{L}{2}\left(
                2\langle L^{-1}\mathcal G_L(y_t), x - y_t\rangle + 
                \Vert x - y_t\Vert^2
            \right)
            \\
            &= 
            \frac{L}{2}
            \left(
                - \Vert L^{-1} \mathcal G_L(y_t)\Vert^2  
                + \Vert L^{-1} \mathcal G_L(y_t)\Vert^2 
                + 
                2\langle L^{-1} \mathcal G_L(y_t), x - y_t\rangle + 
                \Vert x - y_t\Vert^2
            \right)
            \\
            &= \frac{L}{2}\left(
                - \Vert L^{-1}\mathcal G_L(y_t)\Vert^2  
                + \Vert x - (y_t - L^{-1}\mathcal G_L(y_t))
                \Vert^2
            \right), 
        \end{align*}
        therefore it transforms into 
        \begin{align*}
            y_{t + 1} &=\argmin_{x} \left\lbrace
                \frac{L}{2}\left\Vert 
                    x - (y_t - L^{-1}\mathcal G_L(y_t))
                \right\Vert^2
                + \frac{1}{2\eta_{t + 1}}\Vert x - x_{t + 1}\Vert^2
            \right\rbrace
            \\
            &=
            \frac{
                \left(y_t - L^{-1}\mathcal G_L(y_t)\right) + x_{t + 1}
            }{L + \eta_{t + 1}^{-1}}.
        \end{align*}
        Define $z_{t + 1} = y_t - \mathcal G_L(y_t) = \mathcal T_L(y_t)$, which is the proximal gradient set, then the above expression simplifies to 
        $$
        y_{t + 1} = (1 + L\eta_{t +1})^{-1}(x_{t + 1}+ L\eta_{t + 1}z_{t + 1}). 
        $$
    \end{proof}
    \begin{remark}
        $y_{t + 1}$ is the minimizer of a simple quadratic. 
        Given that the original function $h$ is potentially non-smooth, therefore it's not always an upper bound of $h(x)$. 
        The upper bound interpretation of the smooth case as proposed by Ahn \cite{ahn_understanding_2022}, Sra for the update of $y_{t + 1}$ fails when $h$ is non-smooth! 
    \end{remark}

\section{Generic Lyapunov analysis for Accelerated gradient via PPM}
\label{sec:generic_ag_ppm_lyapunov_analysis}
    The following lemma establish an upper bound for quantities used in the Lypunov functions for the convergence rate of 
    \hyperref[def:ag_prox_grad_generic]
    {definition \ref*{def:ag_prox_grad_generic}}
    \begin{lemma}[Lyapunov Inequality]

@@

            \prox{\phi}(x) = x - \tilde \eta\mathcal G_L \bar x. 

@@

            \tilde \eta 
            \langle \mathcal G_L\bar x, x^+ - \mathcal T_L \bar x\rangle

@@

            \tilde \eta_{t + 1}\langle \mathcal G_L y_t, x_{t + 1} - z_{t + 1}\rangle

@@

            - \frac{1}{2}\Vert \tilde\eta_{t + 1} \mathcal G_L\Vert^2 + 

@@

                1 - \epsilon_{t + 2} + \sqrt{(1 - \epsilon_{t + 2}) + 4 c_{t + 2}}

@@

\printbibliography
\end{document}

>>>>

\section{Introduction}
    Recent works from Ahn and Sra \cite{ahn_understanding_2022} and Nesterov \cite{nesterov_lectures_2018} inspired content in this section.
    They explored the interpretation of Nesterov acceleration as a proximal of an upper surrogate function, and then a lower surrogate function. 
    Inspired by such an interpretation, we generalize the framework to the case of $h = f + g$ with $f$ Lipschitz smooth and $g$ convex and friendly to a proximal operator. 
    \par
    Classical analysis and extension of Nesterov accelerated gradient existed. 
    See \cite{guler_new_1992} for an extension of the Nesterov accelerated gradient method to the proximal point method for convex programming. 
    However the classical analysis found in \cite[chapter 2]{nesterov_lectures_2018} involves the assumption of a specific kind of Lypunov function and cherry picked Nesterov's estimating sequence to assist the proof for the parameters in the algorithm. 
    In Ahn's work however, the complexities are packaged into the PPM interpretation of accelerated gradient. 
    It uses a lemma from Moreau envelope to derive the Lypunov analysis, the sizes, and parameters for several variants of the algorithm. 
    \par
    Numerous notable variations of Nesterov accelerated gradient exists. \cite[(6.1.19)]{nesterov_lectures_2018} described a variant of accelerated gradient restricted to a convex domain $Q$. 
    Beck and Toubolle \cite{beck_fast_2009} introduced a variant the problem type of smooth plus non-smooth, known as FISTA. 
    For a variant of accelerated gradient where the iterates converge, see \cite{chambolle_convergence_2015}. 
    Extension such as the Harpen acceleration for the resolvent operator in general is outside of the scope since doesn't have a Moreau envelope. 
    \par
    A wide varieties of interpretation for the Nesterov accelerated gradient exist in the literatures. 
    Consult \cite{su_differential_2015} for a dynamical system interpretation of Nesterov acceleration. 
    The dynamical system interpretation of the algorithm however, lead to the valuable insights that restarting the accerlated gradient algorithm would lead to faster convergence rate for the class of strongly convex function. 
    \par
    % The paper is organized as follow: 
    % \begin{enumerate}
    %     \item Section 
    % \end{enumerate}

\section{Preliminaries}\label{sec:preliminaries}
    In this section we introduce the a descent lemma for Proximal Point Method (PPM) in the convex case. 
    We define the proximal gradient mapping $\mathcal T_L$, and gradient mapping $\mathcal G_L$ for function satisfying assumption 
    \ref*{assumption:smooth-nonsmooth-sum}. 
    A lower bound function is identified using the gradient mapping operator and proved in lemma 
    \ref*{lemma:grad_map_linearization}, 
    this is a key component of the proximal point interpretation of the accelerated gradient method. 
    \begin{assumption}\label{assumption:smooth-nonsmooth-sum}
        Let $h = f + g$ where $f, g$ are convex and $f$ is Lipschitz-Smooth. 
    \end{assumption}

    \begin{theorem}[Proximal Descent Inequality]\label{thm:ppm_descent_ineq}
        Let $f: \RR^n \mapsto \overline \RR^n$ $\beta$ be strongly convex with $\beta \ge 0$, fix any $x \in \RR^n$, define $p = \hprox_f(x)$.
        For all $y \in \RR$ it verifies
        $$
            \left(f(p) + \frac{1}{2}\Vert x - p\Vert^2\right)
            - 
            \left(
                f(y) + \frac{1}{2}\Vert x - y\Vert^2 
            \right)
            \le 
            - \frac{(1 + \beta)}{2}\Vert y - p\Vert^2. 
        $$
        Recall: $\hprox_f(x) = \argmin_{u}\left\lbrace f(u) + \frac{1}{2}\Vert u - x\Vert^2 \right\rbrace$. 
    \end{theorem}
    \begin{remark}
        We use this theorem to prove the convergence of the proximal point method. 
        See the proof (\cite{bauschke_convex_2017}, theorem 12.26). 
    \end{remark}

    \begin{definition}[The Gradient Mapping]
        \label{def:gradient_mapping}
        Suppose $h = f + g$ satisfies 
        \hyperref[assumption:smooth-nonsmooth-sum]{assumption \ref*{assumption:smooth-nonsmooth-sum}}. 
        Define the proximal gradient operator
        $$
            \mathcal T_L(x) := \hprox_{L^{-1}g}(x - L^{-1}\nabla f(x)),
        $$
        and the gradient mapping operator
        $$
            \mathcal G_L(x) = L(x - \mathcal T_L(x)). 
        $$
    \end{definition}
    \begin{remark}
        The name ``gradient mapping" comes from \cite[(2.2.54)]{nesterov_lectures_2018}, however, Nesterov was referring to only the case when $g$ is an indicator function of a convex set in his writing. 
        Of course, in Amir Beck \cite[10.3.2]{beck_first-order_nodate}, it has the exact same definition for gradient mapping as the above. 
    \end{remark}

    \begin{lemma}[Gradient Mapping Approximates Subgradient]
        Suppose $h = f + g$ satisfies 
        \hyperref[assumption:smooth-nonsmooth-sum]{assumption \ref{assumption:smooth-nonsmooth-sum}}, 
        let $\mathcal T_L, \mathcal G_L$ be given by 
        \hyperref[def:gradient_mapping]{definition \ref*{def:gradient_mapping}}.
        Then for all $x$, the gradient mapping verifies
        \begin{align*}
            x^+ &= \mathcal T_L(x), 
            \\
            \mathcal G_L(x) = L(x - x^+) &\in  \nabla f(x) + \partial g(x^+). 
        \end{align*}
    \end{lemma}
    \begin{proof}
        Using the resolvent definition of the proximal gradient operator and the fact that the single-valuedness in the convex settings, $x^+$ has relations: 
        \begin{align*}
            x^+ &= [I + L^{-1}\partial g]^{-1}\circ [I - L^{-1}\nabla f](x)
            \\
            [I + L^{-1}\partial g](x^+) &\ni [I - L^{-1}\nabla f](x)
            \\
            x^+ + L^{-1}\partial g(x^+) &\ni x - L^{-1}\nabla f(x)
            \\
            x^+ - x + L^{-1}\partial g(x^+) &\ni L^{-1}\nabla f(x)
            \\
            L(x^+ - x) + \partial g(x^+) &\ni - \nabla f(x)
            \\
            L(x - x^+) &\in \nabla f(x) + \partial g(x^+)
            \\
            \mathcal G_L(x) &\in \nabla f(x) + \partial g(x^+). 
        \end{align*}
    \end{proof}

@@

        Suppose that $h = f + g$ satisfies 
        \hyperref[assumption:smooth-nonsmooth-sum]{assumption \ref*{assumption:smooth-nonsmooth-sum}}, 
        further assume that $f$ is strongly convex with index $\mu \ge 0$. 
        Let $x^+ = \mathcal T_L(x)$ as given in 
        \hyperref[def:gradient_mapping]{definition \ref*{def:gradient_mapping}}. 
        Then for all $z \in \RR$, it satisfies

@@

        Using the $L$-smoothness of $f$ and convexity of $g, f$, it has inequalities

@@

        Apply the above by considering the following sequence of relations

@@

        The inequality is analogous to \cite[(2.2.57)]{nesterov_lectures_2018}. 

@@

\section{The PPM interpreation of accelerated gradient}\label{sec:ppm_interp_of_ag}
    In this section, we present the PPM formulation of the accelerated proximal gradient method. 
    These interpretations of \cite{ahn_understanding_2022} are extension in the non-smooth context using the proximal gradient mapping operator. 
    The next definition starts the discussion. 
    \begin{definition}[Linear Lower Bounding Function]\label{def:gradmap-linear-lowerbnd-fxn}
        Let $h = f+ g$ satisfies
        \hyperref[assumption:smooth-nonsmooth-sum]{definition \ref*{assumption:smooth-nonsmooth-sum}}, 
        $\mathcal G_L$ given by 
        \hyperref[def:gradient_mapping]{definition \ref*{def:gradient_mapping}}. 
        Define for all $y$ the function
        \begin{align*}
            l_h(x; y) = h(\mathcal T_L y) + \langle \mathcal G_L(y), x - y \rangle 
            + \frac{L}{2}\Vert y - \mathcal T_L y\Vert^2. 
        \end{align*}
    \end{definition} 
    \begin{remark}
        The function satisfies $l_h(x; y) \le h(x)$ for all $x \in \RR, y \in \RR$ by 
        \hyperref[lemma:grad_map_linearization]
        {lemma \ref*{lemma:grad_map_linearization}}. 
    \end{remark}
    \par
    With the above definition, it's possible to formulate a generic form of accelerated gradient method using $l_h(x,y)$ as two proximal point methods anchored at some iterates $x_t, x_{t + 1}$.
    The formulation is generic because of undetermined stepsize parameter $\eta_t, \tilde \eta_t$ from the two proximal point. 
    \par
    We state the PPM interpretation of accelerated gradient in 
    \hyperref[def:ag_prox_grad_ppm]{definition \ref*{def:ag_prox_grad_ppm}}, 
    which has the equivalent form as presented in
    \hyperref[def:ag_prox_grad_generic]
    {definition \ref*{def:ag_prox_grad_generic}}. 
    \hyperref[prop:derive_ag_prox_grad_tript]
    {Proposition \ref*{prop:derive_ag_prox_grad_tript}} 
    shows their equivalence. 
    \par
    Throughout this section, we assume 
    \begin{enumerate}
        \item $h=f + g$ satisfies 
            \hyperref[assumption:smooth-nonsmooth-sum]
            {assumption \ref*{assumption:smooth-nonsmooth-sum}}, 
        \item Using $h$ as given from above, let $\mathcal T_L, \mathcal G_L$ be given by 
            \hyperref[def:gradient_mapping]
            {definition \ref*{def:gradient_mapping}}. 
        \item Using all above, let $l_h$ be given by 
            \hyperref[def:gradmap-linear-lowerbnd-fxn]
            {definition \ref*{def:gradmap-linear-lowerbnd-fxn}}. 
    \end{enumerate}

    \begin{definition}[AG Proximal Gradient PPM Generic Form]
    \label{def:ag_prox_grad_ppm}
        Define $\eta_t, \tilde \eta_t$ to be $> 0$ for all $t \in \N$. 
        With initial iterate $x_0, y_0$, 
        The generic form has iterates $x_t, y_t$ for all $t \in \N$ that satisfy: 
        $$
        \begin{aligned}
            x_{t + 1} &= \argmin_{x} \left\lbrace
                l_h(x; y_t) + \frac{1}{2\tilde \eta_{t + 1}} 
                \Vert x - x_t\Vert^2
            \right\rbrace,
            \\
            y_{t + 1}&= 
            \argmin_{x}
            \left\lbrace
                l_h(x; y_t) + \frac{L}{2}\Vert x - y_t\Vert^2 + 
                \frac{1}{2\eta_{t + 1}} \Vert x - x_{t + 1}\Vert^2
            \right\rbrace.
        \end{aligned}
        $$

    \end{definition}

    \begin{definition}[AG Proximal Gradient Generic Form]
    \label{def:ag_prox_grad_generic}
        Define $\eta_t, \tilde \eta_t$ to be $> 0$ for all $t \in \N$. 
        With initial iterate $x_0, y_0$.
        The generic form has iterates $(y_t, x_{t + 1}, z_{t + 1})$ such that 
        $$
        \begin{aligned}
            y_t^+ &= \mathcal T_L(y_t)
            \\
            y_t &= (1 + L\eta_t)^{-1}(x_t + L\eta_t z_t)
            \\
            x_{t + 1} &= x_t - \tilde \eta_{t + 1} \mathcal G_L(y_t)
            \\
            z_{t + 1} &= y_t - L^{-1}\mathcal G_L(y_t)
        \end{aligned}
        $$
        for all $t\in \mathbb N$. 
    \end{definition}
    \begin{remark}
        Observe that $z_{t + 1} = y_t^+$. 
    \end{remark}

    \begin{proposition}
    \label{prop:derive_ag_prox_grad_tript}
       We have equalities
        \begin{align*}
            x_{t + 1} &= \argmin_{x}
            \left\lbrace
                l_h(x, y_t) + \frac{1}{2\tilde \eta_{t + 1}} \Vert x - x_t\Vert^2
            \right\rbrace
            \\
            &= x_t - \tilde\eta_{t + 1} \mathcal G_L(y_t), 
            \\
            y_{t + 1} &= \argmin_{x}
            \left\lbrace
                    h(y_t^+) + \langle \mathcal G_L(y_t), x - y_t\rangle + \frac{L}{2}\Vert x -y_t\Vert^2 + \frac{1}{2\eta_{t + 1}}\Vert x - x_{t + 1}\Vert^2
            \right\rbrace
            \\
            &= (1 + L\eta_{t + 1})^{-1}
            (x_{t + 1} + L\eta_{t + 1}(y_t - L^{-1}\mathcal  G_L(y_t))). 
        \end{align*}
        This thows
        \hyperref[def:ag_prox_grad_ppm]{definition \ref*{def:ag_prox_grad_ppm}}
        and 
        \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}} 
        are equivalent. 
    \end{proposition}
    \begin{proof}
        Let $y_t^+ = \mathcal T_L(y_t)$, recall that $l_h(x; y_t) = h(y_t^+) + \langle \mathcal G_L(y_t), x -y_t\rangle \le f(x)$ by 
        \hyperref[lemma:grad_map_linearization]
        {lemma \ref*{lemma:grad_map_linearization}}
        Since $l_h(x; y_t)$ is a simple linear function wrt $x$, minimizing the quandratic where to get $x_{t + 1} = x_t - \tilde\eta_{t + 1} \mathcal G_L(y_t)$; for $y_{t + 1}$, complete the square on the second and the third terms: 
        \begin{align*}
            & \frac{L}{2}\left(
                2\langle L^{-1}\mathcal G_L(y_t), x - y_t\rangle + 
                \Vert x - y_t\Vert^2
            \right)
            \\
            &= 
            \frac{L}{2}
            \left(
                - \Vert L^{-1} \mathcal G_L(y_t)\Vert^2  
                + \Vert L^{-1} \mathcal G_L(y_t)\Vert^2 
                + 
                2\langle L^{-1} \mathcal G_L(y_t), x - y_t\rangle + 
                \Vert x - y_t\Vert^2
            \right)
            \\
            &= \frac{L}{2}\left(
                - \Vert L^{-1}\mathcal G_L(y_t)\Vert^2  
                + \Vert x - (y_t - L^{-1}\mathcal G_L(y_t))
                \Vert^2
            \right), 
        \end{align*}
        therefore it transforms into 
        \begin{align*}
            y_{t + 1} &=\argmin_{x} \left\lbrace
                \frac{L}{2}\left\Vert 
                    x - (y_t - L^{-1}\mathcal G_L(y_t))
                \right\Vert^2
                + \frac{1}{2\eta_{t + 1}}\Vert x - x_{t + 1}\Vert^2
            \right\rbrace
            \\
            &=
            \frac{
                \left(y_t - L^{-1}\mathcal G_L(y_t)\right) + x_{t + 1}
            }{L + \eta_{t + 1}^{-1}}.
        \end{align*}
        Define $z_{t + 1} = y_t - \mathcal G_L(y_t) = \mathcal T_L(y_t)$, which is the proximal gradient set, then the above expression simplifies to 
        $$
        y_{t + 1} = (1 + L\eta_{t +1})^{-1}(x_{t + 1}+ L\eta_{t + 1}z_{t + 1}). 
        $$
    \end{proof}
    \begin{remark}
        $y_{t + 1}$ is the minimizer of a simple quadratic. 
        Given that the original function $h$ is potentially non-smooth, therefore it's not always an upper bound of $h(x)$. 
        The upper bound interpretation of the smooth case as proposed by Ahn \cite{ahn_understanding_2022}, Sra for the update of $y_{t + 1}$ fails when $h$ is non-smooth! 
    \end{remark}

\section{Generic Lyapunov analysis for Accelerated gradient via PPM}
\label{sec:generic_ag_ppm_lyapunov_analysis}
    The following lemma establish an upper bound for quantities used in the Lypunov functions for the convergence rate of 
    \hyperref[def:ag_prox_grad_generic]
    {definition \ref*{def:ag_prox_grad_generic}}
    \begin{lemma}[Lyapunov Inequality]. 
    The Lypunov function in use is identical to Ahn and Sra \cite[section 4.2]{ahn_understanding_2022} except for the involvement of a gradient mapping. 
    We present the results differently by compatifying results into 
    \hyperref[lemma:nsmooth_agg_lyapunov_upper_bound]
    {lemma \ref*{lemma:nsmooth_agg_lyapunov_upper_bound}}. 
    Theorem \ref*{thm:generic_ag_convergence} 
    states new results that are extension to Ahn and Sra's works by introducing an error term to the Lypunov analysis, allowing for a weaker constraints for the stepsize paramters $\tilde \eta_i, \eta_i$ from 
    \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}}. 
    \par
    Theorem \ref*{thm:ag_generic_stepsize_constrants} states the weakened constraints on the stepsize parameters $\tilde \eta_i, \eta_i$.

@@

            \hprox_\phi(x) = x - \tilde \eta\mathcal G_L \bar x. 

@@

            - \tilde \eta \langle \mathcal G_L\bar x, x^+ - \mathcal T_L \bar x\rangle

@@

            - \tilde \eta_{t + 1}\langle \mathcal G_L y_t, x_{t + 1} - z_{t + 1}\rangle

@@

            - \frac{1}{2}\Vert \tilde\eta_{t + 1} \mathcal G_L(y_t)\Vert^2 + 

@@

                1 - \epsilon_{t + 2} + \sqrt{(1 - \epsilon_{t + 2}) + 4 c_{t + 1}}

@@

% \printbibliography

\bibliographystyle{siam}
\bibliography{references/refs}

\end{document}
